Impute missing values of training and validation data using multiple imputation

### 2023-02-09 Code/0_PrepareValidationData.Rmd
Added analysis with pooled data

#### Delete unused levels
```{r, eval=TRUE}
sel.val.data <- droplevels(sel.val.data)
sel.val.data$Center <- "Australia"
```

@@

# Multiple imputation
```{r, eval=TRUE}
variables.to.be.imputed <- c("Center", "SNstatus", "Sex", "Age.SN", "Ulceration",
                             "Loc_CAT", "Histology", "Breslow", "multiple.fields",
                             "Tot_SNs_neg", "Tot_SNs_pos", "Rdamcrit", "Dewar",
                             "Mitosis",
                             "Recurrence", "dead", "MSM", "Rec.time", "FU.time")
validation.data.to.be.imputed <- sel.val.data[, variables.to.be.imputed]
```

>>>>

#### Delete unused levels
```{r, eval=TRUE}
sel.val.data <- droplevels(sel.val.data)
sel.val.data$Center <- 5
sel.val.data$Center <- factor(sel.val.data$Center, labels = c("Australia"))
```

@@

# Multiple imputation
```{r, eval=TRUE}
variables.to.be.imputed <- c("Center", "SNstatus", "Sex", "Age.SN", "Ulceration",
                             "Loc_CAT", "Histology", "Breslow", "multiple.fields",
                             "Tot_SNs_neg", "Tot_SNs_pos", "Rdamcrit", "Dewar",
                             "Mitosis",
                             "Recurrence", "dead", "MSM")
validation.data.to.be.imputed <- sel.val.data[, variables.to.be.imputed]
```

### 2023-02-09 Code/1_DescriptivesTable.Rmd
Validation added
Added analysis with pooled data

library(arsenal)
library(knitr)

load("Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata")
load("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata")
descr.table <- arsenal::tableby(Center ~ SNstatus
                                +Sex
                                +Age.SN
                                +arsenal::includeNA(Ulceration)
                                +arsenal::includeNA(Loc_CAT)
                                +arsenal::includeNA(Histology)
                                +Breslow
                                +multiple.fields
                                +Tot_SNs_neg
                                +Tot_SNs_pos
                                +Rdamcrit
                                +arsenal::includeNA(Dewar)
                                +arsenal::includeNA(Mitosis)
                                +Recurrence
                                +dead
                                +MSM
                                +logRec.time
                                +logFU.time, data=rbind(training.data.to.be.imputed, validation.data.to.be.imputed[, -c(18, 19)]), # training.data.to.be.imputed,
                                total.pos="before",
                                digits = 1,
                                test = F,
                                total = T,
                                numeric.test = "kwt", cat.test = "chisq",
                                numeric.stats = c("meansd", "medianq1q3", "range", "Nmiss2"),
                                cat.stats = c("countpct"),
                                stats.labels = list(
                                  meansd = "Mean (SD)",
                                  medianq1q3 = "Median (Q1, Q3)",
                                  range = "Min - Max",
                                  Nmiss2 = "Missing"
                                ))
my_labels <- list(
  SNstatus = "SN status",
  Age.SN = "Age",
  Loc_CAT = "Location",
  multiple.fields = "Multiple fields",
  Tot_SNs_neg = "Total number of negative SN",
  Tot_SNs_pos = "Total number of positive SN",
  Rdamcrit = "SN tumour burden",
  Dewar = "Location metastasis in lymph",
  dead = "Deaths",
  MSM = "Melanoma specific mortality"
)
```

>>>>

# load packages
library(arsenal)
library(knitr)

load("Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata")
load("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata")
descr.table <- arsenal::tableby(Center ~ SNstatus
                                +Sex
                                +Age.SN
                                +arsenal::includeNA(Ulceration)
                                +arsenal::includeNA(Loc_CAT)
                                +arsenal::includeNA(Histology)
                                +Breslow
                                +multiple.fields
                                +Tot_SNs_neg
                                +Tot_SNs_pos
                                +Rdamcrit
                                +arsenal::includeNA(Dewar)
                                +arsenal::includeNA(Mitosis)
                                +Recurrence
                                +dead
                                +MSM
                                +logRec.time
                                +logFU.time, data=rbind(training.data.to.be.imputed, validation.data.to.be.imputed), # training.data.to.be.imputed,
                                total.pos="before",
                                digits = 1,
                                test = F,
                                total = T,
                                numeric.test = "kwt", cat.test = "chisq",
                                numeric.stats = c("meansd", "medianq1q3", "range", "Nmiss2"),
                                cat.stats = c("countpct"),
                                stats.labels = list(
                                  meansd = "Mean (SD)",
                                  medianq1q3 = "Median (Q1, Q3)",
                                  range = "Min - Max",
                                  Nmiss2 = "Missing"
                                ))
my_labels <- list(
  SNstatus = "SN status",
  Age.SN = "Age",
  Loc_CAT = "Location",
  multiple.fields = "Multiple fields",
  Tot_SNs_neg = "Total number of negative SN",
  Tot_SNs_pos = "Total number of positive SN",
  Rdamcrit = "SN tumour burden",
  Dewar = "Location metastasis in lymph",
  dead = "Deaths",
  MSM = "Melanoma specific mortality"
)
```

### 2023-02-09 Code/2_ImputeData.Rmd
Validation added
Added analysis with pooled data

---
title: "Impute missing values of training and validation data using multiple imputation"
author: "Carolien C.H.M. Maas"
date: "December 2022"
output: html_document
---

@@

Function to perform multiple imputation for training or validation data
```{r, eval=TRUE}
impute.missing.values <- function(type=NULL, m=1, new.imputation=FALSE){
  # load data
  load(paste0("Z:/Project Melanoom/PaperMelanoma/Data/", type, "/", type, ".data.Rdata"))

@@

Perform multiple imputation
```{r, eval=TRUE}
# erase memory
m <- 5
new.imputation <- TRUE
# Impute: Ulceration, Loc_CAT, Histology, Breslow, Tot_SNs_neg, Tot_SNs_pos, Rdamcrit, Dewar, Mitosis, logRec.time
impute.missing.values(type="training", m=m, new.imputation=new.imputation)
# Impute: Ulceration, Histology, Rdamcrit, Dewar, logRec.time
impute.missing.values(type="validation", m=m, new.imputation=new.imputation)

>>>>

---
title: "Impute missing values of training and validation data using multiple imputation"
author: "Carolien C.H.M. Maas"
date: "January 2023"
output: html_document
---

@@

Function to perform multiple imputation for training or validation data
```{r, eval=TRUE}
impute.missing.values <- function(type=NULL, m=1, new.imputation=FALSE){
  # load data
  if (type=="pooled"){
    load(paste0("Z:/Project Melanoom/PaperMelanoma/Data/training/training.data.Rdata"))
    load(paste0("Z:/Project Melanoom/PaperMelanoma/Data/validation/validation.data.Rdata"))
    pooled.data.to.be.imputed <- rbind(training.data.to.be.imputed, validation.data.to.be.imputed)
    dd.pooled<-rms::datadist(pooled.data.to.be.imputed)
  } else{
    load(paste0("Z:/Project Melanoom/PaperMelanoma/Data/", type, "/", type, ".data.Rdata"))
  }

@@

Perform multiple imputation
```{r, eval=TRUE}
# erase memory
m <- 5
new.imputation <- TRUE
# Impute: Ulceration, Loc_CAT, Histology, Breslow, Tot_SNs_neg, Tot_SNs_pos, Rdamcrit, Dewar, Mitosis, logRec.time
impute.missing.values(type="training", m=m, new.imputation=new.imputation)
# Impute: Ulceration, Histology, Rdamcrit, Dewar, logRec.time
impute.missing.values(type="validation", m=m, new.imputation=new.imputation)
# Impute pooled data
# impute.missing.values(type="pooled", m=m, new.imputation=new.imputation)
